Figures for 'Detecting' Manuscript

### 2023-07-25 figures_draft.Rmd
tweak some figures

![Figure 2. Distribution of relationship estimates ($beta_{env}$) in three different "windows" of lambda values. The dashed vertical line is the known relationship value of -0.5.](figures/lambda_angle_plot.png)

@@

![Figure 4. Distribution of relationship estimates (beta_1) when estimating from different known relationships](figures/vary_beta_density_plot.png)

![Figure 5. of empirical data estimates. All of the methods estimate the same sign of the relationship, but the estimates from the binning methods are generally greater than the MLE estimates.](figures/empirical_combined.png)

>>>>

![Figure 2. Distribution of relationship estimates ($\beta_{env}$) in three different "windows" of lambda values. The dashed vertical line is the known relationship value of -0.5.](figures/lambda_angle_plot.png)

@@

![Figure 4. Distribution of relationship estimates ($\beta_{env}$) when estimating from different known relationships](figures/vary_beta_density_plot.png)

![Figure 5. Estimates of change in exponent for size-abundance relationships across gradients from empirical data estimates. Panels A and C show the individual λ estimates for each site and the the line shows the estimated relationship based on method (color) for the natural pollution and temperature gradients, respectively. Panels B and D show the mean estimated relationship coefficient ($\beta$, point) ± 1 standard deviation (error bars) from the OLS model for both empirical data sets. All the methods estimate the same sign of the relationship, but the estimates from the binning methods are generally larger than the MLE estimates.](figures/empirical_combined.png)
